---
title: 'Replication #4'
author: "Jack Schroeder"
date: "4/1/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# I'm still not entirely sure what the rm function is doing here
# (I know it removes objects), but I'm keeping it until I know
# for sure I don't need it.

rm(list = ls())

# I also call in tidyverse in case I need it later on.

library(tidyverse)

# I also load in the csv files Enos calls for. I make sure to turn
# equals signs into <-. I keep the reads in as read.csv as to not
# mess too much with the data.

wtreat <- read.csv('enos_files/white.treat.effect.mean.boot.csv') 
wtreat.lower <- read.csv('enos_files/white.treat.effect.conf.boot.lower.csv') 
wtreat.upper <- read.csv('enos_files/white.treat.effect.conf.boot.upper.csv') 
Nwtreat <- read.csv('enos_files/white.treat.N.csv')
btreat <- read.csv('enos_files/black.treat.effect.mean.boot.csv') 
btreat.lower <- read.csv('enos_files/black.treat.effect.conf.boot.lower.csv') 
btreat.upper <- read.csv('enos_files/black.treat.effect.conf.boot.upper.csv') 
Nbtreat <- read.csv('enos_files/black.treat.N.csv')
distdat <- read.csv('enos_files/predicted.results.distance.vary.context.csv')
areadat <- read.csv('enos_files/predicted.results.area.vary.context.csv')
groups <- read.csv('enos_files/par.trends.csv')
dists <- read.csv('enos_files/distance.vote.differences.csv')
demos <- read.csv('enos_files/demolished.vote.differences.csv')

# There are other csvs read in, but they are all in for loops.
# Since Enos gives them similar names, I don't want to mess with
# them yet.

# I like Enos' for loop that turns the tibbles into matrices (which I
# guess for him are easier to use). I'll keep it in for now.

for(i in 1:nrow(wtreat)){
	use.wtreat <- as.matrix(wtreat[i,])
	use.wlower <- as.matrix(wtreat.lower[i,])
	use.wupper <- as.matrix(wtreat.upper[i,])
	use.Nwtreat <- as.matrix(Nwtreat[i,])
	use.btreat <- as.matrix(btreat[i,])
	use.blower <- as.matrix(btreat.lower[i,])
	use.bupper <- as.matrix(btreat.upper[i,])
	use.Nbtreat <- as.matrix(Nbtreat[i,])

```

## Abstract
I replicate Enos' "What the Demolition of Public Housing Teaches Us about the Impact of Racial Threat on Political Behavior" using the author's replication data from the Harvard Dataverse (@Enos_rep_data). @Enos2015's figures replicate, but his table cannot be recreated since the necessary dataset is not included in the Dataverse.  

```{r master parameters, echo=FALSE}

# Enos sets certain parameters for the graphics that follow.
# I keep them as they are.

# These are setting limits on the axes and setting other values
# for the x and y axes.

ylims = c(-.35,.1)
ylims.2 = c(-.45,.1)
xlims = c(.5,11)
dists = seq(from = 1000, to = 100, by = -100)
xs = seq(1:length(dists))
ys = seq(from = -.35, to = .1, by = .05)
ys.lab = c('-0.35','-0.30', '-0.25','-0.20','-0.15','-0.10','-0.05','0.00','0.05','0.10')
ys.2 = seq(from = -.45, to = .1, by = .05)
ys.lab.2 = c('-0.45','-0.40','-0.35','-0.30', '-0.25','-0.20','-0.15','-0.10','-0.05','0.00','0.05','0.10')

# This code helps out when text, lines, and points are added to
# graphs.

offsets = .15
text.offsets = .025
cex.axis = .9
cex.N = .7
top.text.adj = c(1.3,1.3)
bottom.text.adj = c(-.15,-.85)
point.size = 2
line.offset = .0175

# Enos also sets this code aside for when he has to use letters.

use.letters <- c('a','b','c','d','e','f','skip','g','h')

```

## Replication

### Figure 1. Treatment Effects

```{r figure 1, echo=FALSE}

# The general code to create the graph. He first sets parameters and 
# then creates the actual graph using a matrix he created above.

# He also relies on some of his general parameters (ylims, xlims).

	par(las = 1)
	par(mar = c(5.1, 4.1, .5, .5))
	plot(xs, use.wtreat,
		ylim = ylims,
		xlim = xlims,
		type = 'n',
		ylab = 'Treatment Effect',
		xlab = 'Treated Group Distance from Projects',
		xaxt = 'n',
		yaxt = 'n.csv')
	abline(h = 0, lty = 2)
	
# His justification for having this code above the point creation is
# that he wants the lines drawn and the points put on top. There has
# to be a better way to do this (especially when he creates spacing 
# specifically for the N values). He offsets the black and white voter
# data so they do not appear on top of one another.
	
	segments(x0= xs[1:2]+offsets, x1 = xs[1:2]+offsets,
		y0 = use.btreat[,1:2], y1 =	use.blower[,1:2])
	segments(x0= xs[1:2]+offsets, x1 = xs[1:2]+offsets,
		y0 = use.btreat[,1:2] + line.offset, 	y1 =	use.bupper[,1:2])
	segments(x0= xs[3:10]+offsets, x1 = xs[3:10]+offsets,
		y0 = use.blower[,3:10], 	y1 =	use.bupper[,3:10])
		
# Enos creates the top and bottom lines.
	
	segments(x0= xs-offsets, x1 = xs-offsets,
		y0 = use.wtreat - line.offset, 	y1 =	use.wlower)
	segments(x0= xs-offsets, x1 = xs-offsets,
		y0 = use.wtreat, 	y1 =	use.wupper)

  
# Enos uses this code to make the points on the graph and display the
# proper N values. It's worth noting that this is a cumulative graph.

	points(xs-offsets, use.wtreat,
	       cex = point.size,
	       pch = 21, 
	       bg = 'white',
	       col = 'black')
	text(xs-offsets,use.wtreat,
	     paste('(',use.Nwtreat,')',sep = ''),
	     cex = cex.N,
	     pos = 1
	    )
	
	points(xs+offsets, use.btreat,
	       pch = 16,
	       cex = point.size)
	text(xs+offsets,use.btreat,
	     paste('(',use.Nbtreat,')',sep = ''),
	     cex = cex.N,
	     pos = 3
	    )

# Now Enos works on formatting the axes.
	
	axis(side = 1,
		at = xs,
		label = seq(100,1000,100),
		cex.axis = cex.axis
		)
	axis(side = 2,
		at = ys,
		label = ys.lab,
		cex.axis = cex.axis
		)

```

### Figure 2. Treatment Effects Using Matched White Voters Near Nondemolished Projects for Control Group

### Figure 3. Treatment Effects Using Matched Black Control Group and Controlling for Homeownership

```{r figure 2, echo=FALSE}

###########################################
###matched groups################
###Figures 2 and 3 and Appendix Figure A3-A12
###################################

##this cycles thorugh a bunch of dataframes, each of which is needed for a different graph
for(figure in c('white.basic.main','white.demo.main','white.demo.property','white.demo.localrace','blackmain','blackcensus')){
	if(figure == 'white.basic.main'){
		##this group is different than the rest because the second set is not actually a diff in diff, but calling it "diffs" for consistency
		treat <- read.csv('enos_files/white.match.basic.csv')
		treat.2 <- read.csv('enos_files/white.match.basic.property.csv')
		fig.nums = c('A3','A4') ##figure names
		pchs = c(17,17) ##point types
		}
	if(figure == 'white.demo.main'){
		treat <- read.csv('enos_files/white.match.nondemolished.csv')
		diffs <- read.csv('enos_files/white.match.nondemolished.diffs.csv')
		fig.nums = c('2','A5')
		pchs = c(17,22)
		}
	if(figure == 'white.demo.property'){
		treat <- read.csv('enos_files/white.match.nondemolished.property.csv')
		diffs <- read.csv('enos_files/white.match.nondemolished.diffs.property.csv')
		fig.nums = c('A6','A7')	
		pchs = c(17,22)
		}	
	if(figure == 'white.demo.localrace'){
		treat <- read.csv('enos_files/white.match.nondemolished.localrace.csv')
		diffs <- read.csv('enos_files/white.match.nondemolished.diffs.localrace.csv')
		fig.nums = c('A8','A9')			
		pchs = c(17,22)
		}
	if(figure == 'blackmain'){
		treat <- read.csv('enos_files/white.match.black.property.csv')
		diffs <- read.csv('enos_files/white.match.black.diffs.property.csv')
		fig.nums = c('3','A12')
		pchs = c(17,21)			
		}
	if(figure == 'blackcensus'){
		treat <- read.csv('enos_files/white.match.black.csv')
		diffs <- read.csv('enos_files/white.match.black.diffs.csv')
		fig.nums = c('A10','A11')
		pchs = c(17,21)	
		}


	##define axis for different graphs
	if(figure %in% c('white.basic.main','white.demo.main','blackmain')){
			use.ylims = ylims
			use.ys.lab = ys.lab
			use.ys = ys
		}
	else{
			use.ylims = ylims.2
			use.ys.lab = ys.lab.2
			use.ys = ys.2
		}

	##go through pairs for each pair of dataframe
	for(i in 1:2){
		if(i == 1){ 	
			use.treat = treat$coefficient			
			clower = use.treat-(1.96*treat$stdev)
			cupper = use.treat+(1.96*treat$stdev)
			use.N.treat = treat$N.treatment + treat$N.control
			}			
		if(i == 2 & figure != 'white.basic.main'){	
			use.treat = diffs$mean.diff			
			clower = diffs$low.ci
			cupper = diffs$high.ci
			use.N.treat = diffs$N
			}	
		if(i == 2 & figure == 'white.basic.main'){	##white.basic.main figures have slightly different structure 
			use.treat = treat.2$coefficient			
			clower = use.treat- (1.96*treat.2$stdev)
			cupper = use.treat+(1.96*treat.2$stdev)
			use.N.treat = treat.2$N.treatment + treat.2$N.control
			}
		if(figure %in% c('white.demo.main','blackmain') & i ==1){
				pdf(paste('figures/Figure_',fig.nums[i],'.pdf',sep=''))
				}
		else{	
			pdf(paste('figures/Figure_',fig.nums[i],'.pdf',sep=''))
			}
			par(las = 1)
			par(mar = c(5.1, 4.1, .5, .5))
			plot(xs, use.treat,
				ylim = use.ylims,
				xlim = xlims,
				type = 'n',
				ylab = 'Treatment Effect',
				xlab = 'Treated Group Distance from Projects',
				xaxt = 'n',
				yaxt = 'n')
			abline(h = 0, lty = 2)
				
			segments(x0=xs,x1=xs,
						y0= use.treat+line.offset,y1=cupper)
			segments(x0=xs,x1=xs,
						y0= use.treat,y1=clower)

		### Treatment Effects
			points(xs, use.treat, 
				pch = pchs[i], 
				cex = point.size,
					bg = 'white',
       			col = 'black')
			text(xs,use.treat,
			     paste('(',use.N.treat,')',sep = ''),
			     cex = cex.N,
			     pos = 3
			  )
			axis(side = 1,
					at = xs,
					label = seq(100,1000,100),
					cex.axis = cex.axis
					)
			axis(side = 2,
					at = use.ys,
					label = use.ys.lab,
					cex.axis = cex.axis
					)	
			
			dev.off()
		}
}	

```

### Figure 4. Effects of Distance and Size of Projects

```{r figure 4, echo=FALSE}


###########################################
###regression of turnout on distance and population size################
###Figure 4
###################################
##write out regression to latex table
#load('enos_files/out.reg.predictions.rda') ##load saved model
#out.model = apsrtable(out.reg.predictions,
#	coef.names = c( 'Intercept','log(distance)','log(percent of local black population)','2000 turnout'),
#	digits = 3
#	)
#writeLines(out.model,
#	'output/Table_1.tex')
	

###########################################
###predicted effects graphs################
###Figure 4
###################################



##new ylims for these graphs
ylims.predict = c(.6,.75)

datas = list(distdat,areadat)##put data in a list to cycle through
##parameters to be used in graphs below
xs = list(seq(from = 10, to = 2000, by = 10), seq(from = 45000, to = 1004000, by = 4800)/1000)
use.letters = c('a','b')
xlabs = c('Distance from Project','Percent of Local Black Population in Demolished Project')
ylabs = c(expression(Pr(vote[2004])),'')
vlines = list(seq(from = 0, to = 2000, by = 200),seq(from = 0, to = 1000, by = 100))
axis.labs = list(as.character(seq(from = 0, to = 2000, by = 200)),
	as.character(c('0','10%','20%','30%','40%','50%','60%','70%','80%','90%','100%')))

for(i in 1:2){
	colnames(datas[[i]]) = c("mean","sd","50%","2.5%","97.5%") ##saving renames columns, so name back

	pdf(paste('figures/Figure_4',use.letters[i],'.pdf',sep=''))
		par(las = 1)
		par(mar = c(5.1, 4.1, .5, .5))
		plot(xs[[i]],datas[[i]][,'mean'],
			type = 'l',
			xlab = xlabs[i],
			ylab = ylabs[i],
			ylim = ylims.predict,
			xaxt = 'n',
			cex.axis = cex.axis,
			lwd = 4
		)
	##put horizontal and vertical lines on plots
	abline(h = seq(from = min(ylims.predict), to = max(ylims.predict), by = .025),
	       lty = 2,
	       col = 'gray',
	       lwd = 1)
	abline(v = vlines[[i]], 
	       lty = 2,
	       col = 'gray',
	       lwd = 1)
	lines(xs[[i]],datas[[i]][,'2.5%'],
			lty = 3,
			lwd = 2.5)
	lines(xs[[i]],datas[[i]][,'97.5%'],
			lty = 3,
			lwd = 2.5)
	axis(side = 1, 
		at = vlines[[i]], 
		labels = axis.labs[[i]],
		cex.axis = cex.axis)
		
		dev.off()
	}

```

### Figure 5. Difference in Republican Vote for Matched Precincts

### Figure 6. Difference in Obama Vote for Matched Precincts

```{r figure 5, echo=FALSE}


###########################################
###vote choice graphs################
###Figures 5 and 6
###################################
pres.elections = c('dole_pct_ei','bush2000_pct_ei','bush2004_pct_ei','mccain_pct_ei')
obama.elections = c('obama_sen_primary_pct_ei','keyes_pct_ei','obama_pres_primary_pct_ei')




graphs = c('5a','5b','6')

for(i in graphs){

	if(i == '5a'){dat = dists}
	else{dat = demos}
		
	if(i %in% c('5a','5b')){
		xlims = c(.75,4.25)
		ylims = c(-.1,.2)	
		}
	else{
		xlims = c(.75,3.25)
		ylims = c(-.1,.25)
		}

	##recode Keyes to Obama general for presentation purposes
	dat[dat$election == 'keyes_pct_ei','x.mean'] = 1 - dat[dat$election == 'keyes_pct_ei','x.mean']
	dat[dat$election == 'keyes_pct_ei','y.mean'] = 1 - dat[dat$election == 'keyes_pct_ei','y.mean']
	dat[dat$election == 'keyes_pct_ei','diff'] =dat[dat$election == 'keyes_pct_ei','y.mean'] - dat[dat$election == 'keyes_pct_ei','x.mean']
	
		pdf(paste('figures/Figure_',i,'.pdf',sep=''),
		width = 7, height = 8)
		par(las = 1)
		par(mar = c(5.1, 4.1, .5, 1.5))
		plot(seq(1:4),
			rep(1,4),
			ylim = ylims,
			xlim = xlims, 
			type = 'n',
			xaxt = 'n',
			yaxt = 'n',
			xlab = 'Election',
			ylab = ifelse(i == '5b','','Treatment Effect')
			)
		abline(h=0, lty = 2)
		
		if(i %in% c('5a','5b')){
			segments(
				x0= seq(1:4)-offsets, 
				x1 = seq(1:4)-offsets,
				y0 = dat[dat$group == 'white'&dat$election %in% pres.elections,'diff']-(1.96*dat[dat$group == 'white'&dat$election %in% pres.elections,'sd']),
				y1 =	dat[dat$group == 'white'&dat$election %in% pres.elections,'diff']+(1.96*dat[dat$group == 'white'&dat$election %in% pres.elections,'sd'])	
					)
			points(seq(1:4)-offsets,
				dat[dat$group == 'white'&dat$election %in% pres.elections,'diff'],
					pch = 21, 
					bg = 'white',
					col = 'black',
					cex = 2
				)
			segments(
				x0= seq(1:4)+offsets, 
				x1 = seq(1:4)+offsets,
				y0 = dat[dat$group == 'black'&dat$election %in% pres.elections,'diff']-(1.96*dat[dat$group == 'black'&dat$election %in% pres.elections,'sd']),
				y1 =	dat[dat$group == 'black'&dat$election %in% pres.elections,'diff']+(1.96*dat[dat$group == 'black'&dat$election %in% pres.elections,'sd'])	
					)
			points(seq(1:4)+offsets,
				dat[dat$group == 'black'&dat$election %in% pres.elections,'diff'],
					pch = 16,
					cex = 2
				)
			axis(side = 1, at = seq(1:4), 
				c('1996','2000','2004','2008'), 
				tick = F,
				cex.axis = cex.axis)		
			}
		else{
			segments(
				x0= seq(1:3)-offsets, 
				x1 = seq(1:3)-offsets,
				y0 = dat[dat$group == 'white'&dat$election %in% obama.elections,'diff']-(1.96*dat[dat$group == 'white'&dat$election %in% obama.elections,'sd']),
				y1 =	dat[dat$group == 'white'&dat$election %in% obama.elections,'diff']+(1.96*dat[dat$group == 'white'&dat$election %in% obama.elections,'sd'])	
					)
			points(seq(1:3)-offsets,
				dat[dat$group == 'white'&dat$election %in% obama.elections,'diff'],
					pch = 21, 
					bg = 'white',
					col = 'black',
					cex = 2
				)
			segments(
				x0= seq(1:3)+offsets, 
				x1 = seq(1:3)+offsets,
				y0 = dat[dat$group == 'black'&dat$election %in% obama.elections,'diff']-(1.96*dat[dat$group == 'black'&dat$election %in% obama.elections,'sd']),
				y1 =	dat[dat$group == 'black'&dat$election %in% obama.elections,'diff']+(1.96*dat[dat$group == 'black'&dat$election %in% obama.elections,'sd'])	
					)
  			points(seq(1:3)+offsets,
				dat[dat$group == 'black'&dat$election %in% obama.elections,'diff'],
					pch = 16,
					cex = 2
				)
		axis(side = 1, at = seq(1:3), 
					c('2004 \n Senate Primary','2004 \n Senate General','2008 \n President Primary'),
					tick = F,
					cex.axis = cex.axis
					)
		
			}	
		axis(side = 2,
			at = seq(from = -.1, to = .3, by = .05),
			label = c('-0.10','-0.05','0.00','0.05','0.10','0.15','0.20','0.25','0.30'),
			cex.axis = cex.axis
			)			
		dev.off()
	}		
				


```

